### 2013-10-20 notes/coop.tex
Changes

>>>>

Coalition-game thoery provides suitable analytical tools that have been widely explored in different diciplines such as economics and political sceince. With the recent emergence of cooperation as a new networking paradigm, coalition-game  theory started to become a central framework for modeling cooperation in wireless and communication networks. For instance, coalition games prove to be a very powerful tool for designing fair, robust, practical and efficient cooperation strategies in communication networks.
